### 2012-05-11 inst/examples/policycosts/exact_npv.Rmd

Calculate the transition matrix and intialize the the list of penalty functions and cost levels we will be looping over.
``` {r  }
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
penaltyfns <- list(L2=L2, L1=L1, asy=asymmetric, fixed=fixed, asy2=free_increase)
c2 <- seq(0, 8, length.out = 9)
````

>>>>

Calculate the transition matrix and intialize the the list of penalty functions and cost levels we will be looping over.
``` {r  }
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
penaltyfns <- list(L2=L2, L1=L1, asy=asymmetric, fixed=fixed, asy2=free_increase)
c2 <- seq(0, 22, length.out = 30)
````
